%-------------------------
% Resume in Latex
% Author : Gielo
% Website: https://github.com/sb2nov/resume
% License : MIT
% https://www.overleaf.com/project/6a2ced5d5daa1c3d4120a6d3
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[
    pdftex,
    colorlinks=true,
    urlcolor=RoyalBlue,
    linkcolor=RoyalBlue,
    citecolor=RoyalBlue
]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

\newcommand{\titrule}{\rule[0.5ex]{\linewidth}{1pt}} % horizontal rule for section titles
%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Gielo Joseph Fernandez} & Email : \href{mailto:gielo0111@gmail.com}{gielo0111@gmail.com}\\
  Auckland, New Zealand & Mobile : (+64) 22 153 5568 \\
  \href{https://www.linkedin.com/in/gielojoseph}{linkedin.com/in/gielojoseph} | \href{https://github.com/gielo0111}{github.com/gielo0111} & Visa: Post Study Work Visa (Until May 2029)
\end{tabular*}


%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
  \resumeSubHeadingListStart
    \item\small{
      Software Engineer with over 6 years of experience in software development ranging from verifying complex systems such as automotive ECU components to insurance technology SaaS platforms. Experienced tester executing manual and end-to-end automated testing frameworks. Recently completed a Master of Applied Management in NZ, combining advanced technical skills in TypeScript, Node.js, and Python with a strategic business mindset. Available to start work immediately.
    }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Orcas Consulting Ltd.}{Raglan, New Zealand}
      {Software Engineer Intern}{Nov. 2025 -- Feb. 2026}
      \resumeItemListStart
        \resumeItem{Web Development}
          {Developed web scraping pipelines and modern interface components to support marine location analytics. Available at: \url{https://www.rippleforecast.com/tide}}
        \resumeItem{Web Scraping}
          {Developed Python-based web scraping pipelines to automate the extraction of structured data from third-party sources, reducing manual collection and enabling scalable data ingestion.}
        \resumeItem{Geospatial API}
          {Integrated the Overpass API to retrieve and process geospatial coordinates, supporting location-based analysis and improving data accuracy for internal tools.}
        \resumeItem{Data Optimization}
          {Researched and evaluated geospatial data compression techniques (GeoJSON vs Zarr) to optimize storage and performance when handling large, complex datasets.}
        \resumeItem{Prototyping}
          {Utilized Replit for rapid prototyping, testing, and collaborative cloud-based application development.}
      \resumeItemListEnd

    \resumeSubheading
      {Evidentful}{Cromwell, New Zealand}
      {Junior AI Engineer Intern}{Dec. 2024 -- Mar. 2025}
      \resumeItemListStart
        \resumeItem{Architecture Analysis}
          {Analyzed existing system architecture (frontend and backend) to identify performance and scalability improvement opportunities, delivering actionable team recommendations.}
        \resumeItem{AI Search POC}
          {Designed and built a proof-of-concept for AI-powered search using hybrid keyword and vector retrieval with Meilisearch, demonstrating enhanced semantic search relevance.}
        \resumeItem{Vector Workflows}
          {Implemented vector search workflows to explore embedding-based retrieval, improving the system's ability to handle natural language queries accurately.}
        \resumeItem{Containerization}
          {Containerized applications using Docker to ensure consistent development, testing, and deployment environments across internal projects.}
      \resumeItemListEnd

    \resumeSubheading
      {Manulife / John Hancock}{Makati, Philippines}
      {Full Stack Software Engineer}{Aug. 2021 -- Sept. 2024}
      \resumeItemListStart
        \resumeItem{Full Stack Dev}
          {Designed, developed, and maintained full-stack applications, delivering new features across APIs, UIs, and backend services throughout the software development lifecycle. Available at: \url{https://www.coverme.com/travel-insurance/get-a-quote}}
        \resumeItem{Scrum Leadership}
          {Led Agile ceremonies as acting Scrum Master, facilitating sprint planning, stand-ups, reviews, and retrospectives to improve team delivery via Jira and MS Teams.}
        \resumeItem{Data Pipelines}
          {Built and maintained reporting pipelines for daily accounting reports, ensuring data accuracy by resolving systemic inconsistencies such as force balance and tolerance issues.}
        \resumeItem{Frontend Frameworks}
          {Delivered responsive UI designs using prominent frontend frameworks including React and Vue, utilizing state management, asynchronous API calls, and authentication.}
        \resumeItem{Automation Frameworks}
          {Designed and maintained robust automated test frameworks and scripts to support scalable, repeatable testing across cloud applications using the WebDriverIO library.}
      \resumeItemListEnd

    \resumeSubheading
      {Denso Ten Solutions}{Pasig City, Philippines}
      {Software Tester}{Aug. 2018 -- July 2021}
      \resumeItemListStart
        \resumeItem{Test Execution}
          {Designed and executed manual test cases based on automotive system specifications, ensuring high software quality and close alignment with functional requirements.}
        \resumeItem{MATLAB Simulation}
          {Utilized MATLAB to generate test inputs and expected outputs, significantly improving test coverage and validation accuracy for vehicle parts.}
        \resumeItem{Environment Configuration}
          {Built and configured secure testing environments using IBM Eclipse to support reliable, repeatable validation processes and system log tracking.}
        \resumeItem{Global Collaboration}
          {Communicated with clients and prepared technical system documentation in Japanese, supporting international collaboration and project requirement clarity.}
      \resumeItemListEnd

    \resumeSubheading
      {McDonald's}{Auckland, New Zealand}
      {Kitchen Crew}{Nov. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Adaptability}
          {Actively integrating into the New Zealand workforce while completing Master's studies, demonstrating strong work ethic, team collaboration, and local workplace adaptability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{RippleForecast Tides (Internship)}
      {Developed web scraping pipelines and modern interface components to support marine location analytics. Available at: \url{https://www.rippleforecast.com/tide}}
    \resumeSubItem{CoverMe (Company Project)}
      {Contributed to a full-stack transactional travel insurance platform handling automated quote computations. Available at: \url{https://www.coverme.com/travel-insurance/get-a-quote}}
    \resumeSubItem{SQL Portfolio (Solo Project)}
      {Designed relational databases and analytic dashboards built using Streamlit cloud. Available at: \url{https://gielofernandez-sql-project.streamlit.app/}}
    \resumeSubItem{Employee Attrition Prediction(Masters}
      {Applied Logistic Regression modeling to human resources datasets for predictive workforce analytics during Master's coursework. Hosted on Kaggle: \url{https://www.kaggle.com/code/gelojoseph/predict-employee-attrition-w-logistic-regression}}
    \resumeSubItem{English Subject Website(University}
      {Created a website containing the biographies of me and my teammates. Available at: \url{https://gielo0111.github.io/LagLife_of_Toby_Peds_Gielo/}}
    \resumeSubItem{Reimagined Punta Riviera Resort Website(University)}
      {Modernized and improved the user experience of Punta Riviera Resort website based on user experience principles we have learned. Available at : \url{https://gielo0111.github.io/Punta_Riviera_Resort/}}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Future Skills Academy International}{Auckland, New Zealand}
      {Master of Applied Management; Major in Business Information Systems}{Oct. 2024 -- Apr. 2026}
    \resumeSubheading
      {University of Santo Tomas}{Manila, Philippines}
      {Bachelor of Science in Computer Science}{June 2012 -- July 2017}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: TypeScript, JavaScript, Node.js, Python, Java, C/C++, SQL, VBA/VBS}
     \hfill
     \textbf{Databases}{: SQL, NoSQL, CosmosDB}
   }
   \item{
     \textbf{Frameworks \& Tools}{: React, Redux, NextJS, NestJS, ExpressJS, Docker, Git, CI/CD, Jenkins, Postman}
     \hfill
     \textbf{Testing}{: WebDriverIO, JMeter, NewRelic, TDD}
   }
   \item{
     \textbf{AI \& Cloud}{: Meilisearch, Microsoft Azure (AZ-900), Replit, Lovable, GitHub Copilot}
     \hfill
     \textbf{Methodologies}{: Agile, Scrum Master, Jira}
   }
 \resumeSubHeadingListEnd

%--------CERTIFICATIONS & LANGUAGES------------
\section{Certifications \& Languages}
  \resumeSubHeadingListStart
    \item{
      \textbf{Certifications: } Datacamp AI Fundamentals (2025), Microsoft Certified Azure Fundamentals AZ-900 (2023), AutoCAD Training (2018)
    }
    \item{
      \textbf{Languages: } English (Fluent), Japanese (JLPT N4), Korean (Basic)
    }
  \resumeSubHeadingListEnd

\end{document}
